\documentclass[conference]{IEEEtran}

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs}

\usepackage{hyperref}

\usepackage{microtype}
\setlength{\emergencystretch}{3em}
\Urlmuskip=0mu plus 1mu\relax
\hypersetup{hypertexnames=false}
\hbadness=10000
\vbadness=10000
\raggedbottom

\usepackage{sc26repro}

% PDF-string-safe artifact headings
\renewcommand{\newartifact}{%
    \stepcounter{artifactCounter}%
    \subsection{Computational Artifact
        \texorpdfstring{$A_{\theartifactCounter}$}{A\theartifactCounter}}%
}
\renewcommand{\arteval}[1]{%
    \setcounter{artifactCounter}{#1}%
    \subsection{Computational Artifact
        \texorpdfstring{$A_{#1}$}{A#1}}%
}

% Comment these for final submission:
%\usetag{explanation}
%\usetag{example}

\begin{document}

\twocolumn[%
{\begin{center}
\Huge
Appendix: Artifact Description/Artifact Evaluation
\end{center}}
]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  AD Appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendixAD

\section{Overview of Contributions and Artifacts}

\subsection{Paper's Main Contributions}

\begin{description}
\item[$C_1$] Cross-vendor root-cause analysis: a unified methodology using backward dependence tracing to identify root-cause instructions from stalled instructions across NVIDIA, AMD, and Intel GPUs.
\item[$C_2$] Explicit memory dependency tracing: vendor-specific synchronization edges through AMD \texttt{s\_waitcnt} counters, NVIDIA hardware barrier bits, and Intel SWSB tokens.
\item[$C_3$] Cross-vendor evaluation: geometric-mean speedups of 1.73$\times$--1.82$\times$ across 21 workloads on three GPU platforms, with case studies demonstrating cross-vendor root-cause divergence.
\end{description}

\subsection{Computational Artifacts}

\begin{description}
\item[$A_1$] LEO analysis tool and evaluation infrastructure. Zenodo archive: \url{https://doi.org/10.5281/zenodo.19704349} (concept DOI --- always resolves to the latest release; the reviewed snapshot is tag \texttt{v0.1.4-sc26-ae} at \url{https://doi.org/10.5281/zenodo.19706845}). Pre-collected profiling data (separate deposit, $\sim$1~GB): \url{https://doi.org/10.5281/zenodo.19705577}.
\end{description}

\begin{center}
{\setlength{\tabcolsep}{3pt}
\begin{tabular}{rll}
\toprule
Artifact ID  &  Contributions &  Related \\
             &  Supported     &  Paper Elements \\
\midrule
$A_1$   &  $C_1, C_2, C_3$ & Table IV (per-kernel speedups) \\
        &                   & Table V (LLM diagnostic \\
        &                   & \quad context ablation) \\
        &                   & Figure 5 (SDC coverage) \\
        &                   & Case studies (Sec.~VI) \\
\bottomrule
\end{tabular}}
\end{center}

\bigskip
\noindent\textbf{Badges requested.} We intend to apply for the SC26 badges \emph{Artifacts Available}, \emph{Artifacts Evaluated-Functional}, and \emph{Results Reproduced}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Artifact Identification}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newartifact

\artrel

Artifact $A_1$ contains the LEO analysis tool, Docker-based evaluation infrastructure, benchmark workloads, profiling data, and optimization patches used to produce all experimental results in the paper (Tables~IV--V, Figure~5, and the five case studies in Section~VI: MASS3DEA, miniBUDE, QuickSilver, ML kernels (llama.cpp + HipKittens), and Kripke).

\artexp

For each of the 21 workloads on three GPU platforms, LEO should identify the dominant stall chain through backward dependence tracing. Applying the LEO-guided optimization (confined to the code region implicated by the top-ranked chain) should reproduce the per-kernel speedups reported in Table~IV within measurement noise ($\pm$5\% on NVIDIA and AMD; $\pm$9\% on Intel PVC due to higher platform variability).
The single-dependency coverage (Figure~5) should show improvement from LEO's analysis pipeline on NVIDIA and AMD, with Intel coverage remaining stable due to compiler-verified SWSB edges.
The LLM diagnostic study (Table~V) in the paper evaluates Gemini 3.1 Pro at temperature 0.7 on 15 RAJAPerf CUDA kernels, comparing three diagnostic contexts: code only (C), code plus raw stall counts (C+S), and code plus LEO's structured root-cause analysis (C+L(S)). Table~V's Compilable, Geomean Speedup, and Regressions columns come from a separate compile-and-benchmark harness that requires GPU hardware and is \emph{not} bundled in this artifact. The artifact's \path{--llm-eval} path reproduces the upstream \emph{semantic-match} proxy (does the LLM identify the same root cause that LEO ranks first?), which is what \path{scripts/validation/main.py} implements.

\arttime

\begin{itemize}
\item \textbf{Artifact Setup:} 30--60 min (universal image + per-vendor container builds).
\item \textbf{Artifact Execution:} 2--4 hours per vendor for Table~IV (benchmarking original vs.\ optimized kernels on the target GPU); Figure~5 and Table~V run CPU-only in $\sim$30 min combined. Per-vendor runs are independent and parallelizable across hosts.
\item \textbf{Artifact Analysis:} 15 min (SDC collection + speedup comparison scripts).
\end{itemize}

\artin

\artinpart{Hardware}

Three GPU platforms are required to reproduce all results:
\begin{itemize}
\item \textbf{NVIDIA:} GH200 480GB (sm\_90, Hopper), CUDA 12.8, driver 570+
\item \textbf{AMD:} MI300A (gfx942, CDNA3 APU), ROCm 6.3
\item \textbf{Intel:} Data Center GPU Max 1100 (Ponte Vecchio, Xe-HPC), Level Zero 1.x, oneAPI 2025.1+
\end{itemize}
Partial reproduction on a single vendor is possible; the evaluation scripts support per-vendor execution.

\artinpart{Software}

\begin{itemize}
\item \textbf{LEO} (Python 3.11--3.13, uses \texttt{uv} package manager): bundled in the $A_1$ Zenodo archive; development mirror linked from the Zenodo record metadata.
\item \textbf{HPCToolkit} (branch \path{feature/hidden-stall-metrics}): cloned by the Dockerfiles inside the $A_1$ archive during container build.
\item \textbf{hpcanalysis} (C++ database reader with pybind11): vendored at \path{3rdparty/hpcanalysis/} inside the $A_1$ archive.
\item \textbf{RAJAPerf} v2024.07.0: \url{https://github.com/LLNL/RAJAPerf}
\item \textbf{Docker} 24.0+: all evaluation runs inside vendor-specific containers
\item \textbf{nvdisasm} (CUDA Toolkit), \textbf{llvm-objdump} (ROCm), \textbf{GED} (Intel GTPin 4.5.0): GPU disassemblers, included in Docker images
\item \textbf{Gemini 3.1 Pro via OpenRouter} (\url{https://openrouter.ai}): required only for Table~V reproduction. Needs internet connectivity and a valid \path{OPENROUTER_API_KEY}. Table~IV and Figure~5 do not require LLM access.
\end{itemize}

\artinpart{Datasets / Inputs}

The 21 workloads evaluated in Table~IV consist of 15 RAJAPerf kernels plus 6 HPC/ML applications. HipKittens RMSNorm is additionally studied in Section~VI (not part of Table~IV).

\begin{itemize}
\item \textbf{RAJAPerf kernels (15):} \texttt{Base\_CUDA}, \texttt{Base\_HIP}, and \texttt{Base\_SYCL} variants with default problem sizes, included in RAJAPerf repository. Kernels: MASS3DEA, LTIMES\_NOVIEW, LTIMES, 3MM, 2MM, GEMM, PRESSURE, ENERGY, FIR, ZONAL\_ACCUM\_3D, VOL3D, DEL\_DOT\_VEC\_2D, DIFFUSION3DPA, CONVECTION3DPA, MASS3DPA.
\item \textbf{HPC applications (5):} LULESH, miniBUDE, XSBench, Kripke, QuickSilver --- all open-source with default inputs.
\item \textbf{ML applications (1):} llama.cpp (Qwen2.5-1.5B, Q4\_K\_M quantization).
\item \textbf{Case study:} HipKittens RMSNorm (AMD-only, hand-tuned ML kernel).
\item \textbf{Pre-collected profiling data:} HPCToolkit measurement databases for all 21 workloads $\times$ 3 vendors, collected with the \path{feature/hidden-stall-metrics} HPCToolkit branch on the same hardware listed above (NVIDIA GH200, AMD MI300A, Intel GPU Max 1100), archived in the artifact repository. These enable LEO analysis without access to GPU hardware.
\end{itemize}

\artinpart{Installation and Deployment}

\begin{enumerate}
\item Obtain the artifact: download and extract the tarball from the $A_1$ Zenodo DOI.
\item Install Python dependencies: \texttt{uv sync} (requires Python 3.11--3.13 and GCC 11+ to build the vendored \texttt{hpcanalysis} C++ extension).
\item Download pre-collected HPCToolkit profiling data ($\sim$1~GB compressed, $\sim$5.6~GB extracted): \texttt{bash}~\path{scripts/download_data.sh}.
\item Build the universal analysis container for CPU-only reproduction of Figure~5 and Table~V: \texttt{bash}~\path{scripts/evaluation/build_containers.sh}~\texttt{universal --base-only}. For GPU-side reproduction of Table~IV, reviewers should build vendor-specific containers directly with \texttt{docker build -f}~\path{scripts/evaluation/docker/Dockerfile.rajaperf-<vendor>}~\texttt{-t}~\path{leo-rajaperf-<vendor>}~\texttt{.} on a host with the target GPU; the helper script's non-\texttt{universal} vendors SSH to the authors' Rice cluster and are not portable.
\end{enumerate}

\artcomp

The evaluation workflow consists of four tasks:

\begin{IEEEdescription}[\IEEEsetlabelwidth{$T_3$: Benchmark}]
\item[$T_1$: Profile] Run \texttt{hpcrun} with PC sampling on each workload inside vendor-specific Docker containers. Output: HPCToolkit measurement databases.
\item[$T_2$: Analyze] Run LEO (\path{scripts/analyze_benchmark.py}) on each measurement database. Output: ranked stall chains, dependency graphs, SDC metrics.
\item[$T_3$: Benchmark] Run original vs.\ optimized kernels (\path{benchmarks/rajaperf-h100/run_compare.sh}). Output: per-kernel speedup measurements.
\item[$T_4$: Collect] Run collection scripts (\path{scripts/collect_sdc.sh}, \path{scripts/time_analysis.sh}). Output: SDC coverage data (Figure~5), analysis timing data.
\end{IEEEdescription}

Dependencies: $T_1 \rightarrow T_2 \rightarrow T_4$; $T_1 \rightarrow T_3$. Tasks $T_2$ and $T_3$ can run in parallel after $T_1$ completes.

For pre-collected data (included in artifact), $T_1$ can be skipped entirely, and $T_2$ and $T_4$ can be executed on any x86-64 machine using the universal Docker container without GPU hardware. $T_3$ still requires access to the target GPU to produce fresh speedup measurements; pre-collected timing CSVs in the artifact allow inspection of our baseline numbers without re-running.\footnote{Evaluation parameters: RAJAPerf uses default problem sizes with kernel-specific repetition counts and internal warmup. Case-study applications use 10 independent runs per configuration with mean speedup reported. LEO analysis uses \texttt{--top-n 1} for per-kernel and \texttt{--top-n 5} for whole-program.}

\artout

Raw experimental results are processed by:
\begin{enumerate}
\item \path{scripts/collect_sdc.py}: Extracts per-kernel SDC values from LEO output, generates the data for Figure~5.
\item \path{scripts/plot_sdc_paper.py}: Produces Figure~5 (SDC coverage chart) from collected data.
\item \path{benchmarks/rajaperf-h100/postprocess.py}: Computes speedup ratios from raw timing CSV files for Table~IV.
\item \path{scripts/dump_paper.py}: Generates a full-text markdown dump for review.
\end{enumerate}

\newpage
\appendixAE

\arteval{1}

\artin

Reviewer-facing setup assumes a fresh x86-64 Linux machine with Docker and network access. The four-step enumerate below mirrors \S~Artifact Setup $\to$ Installation and Deployment in the AD; it is duplicated here so reviewers can execute the AE section standalone.

\begin{enumerate}
\item Obtain the artifact: download the tarball from \url{https://doi.org/10.5281/zenodo.19704349} (concept DOI; always resolves to the latest release) and extract it, e.g.\ into \path{~/leo_sc26_ae}.
\item Install \texttt{uv} if not already present: \url{https://astral.sh/uv/install.sh} (shell-install script). Then install Python dependencies: \texttt{uv sync} (Python 3.11--3.13; on RHEL~8, prefix with \texttt{scl enable gcc-toolset-11 --} because the vendored \texttt{hpcanalysis} C++ extension requires GCC~11+).
\item Download pre-collected profiling data: \texttt{bash}~\path{scripts/download_data.sh} ($\sim$1~GB compressed, $\sim$5.6~GB extracted under \texttt{results/}).
\item Build the universal analysis container: \texttt{bash}~\path{scripts/evaluation/build_containers.sh}~\texttt{universal --base-only} ($\sim$20~min one-time; produces the \texttt{leo-base-universal} image used for Figure~5 and Table~V reproduction).
\end{enumerate}

Total setup: approximately 30 minutes of wall-clock time.

\textbf{Environment variables.} Only Table~V reproduction requires one: \path{OPENROUTER_API_KEY} (obtain from \url{https://openrouter.ai}). Figure~5 and Table~IV have no env-var dependencies.

\textbf{GPU prerequisites.} Table~IV and the Section~VI case studies require per-vendor Docker images \path{leo-rajaperf-{nvidia,amd,intel}}. Reviewers on their own GPU host should build these directly: \texttt{docker build -f}~\path{scripts/evaluation/docker/Dockerfile.rajaperf-<vendor>}~\texttt{-t}~\path{leo-rajaperf-<vendor>}~\texttt{.} from the artifact root. The helper \path{scripts/evaluation/build_containers.sh <vendor> --workload rajaperf} is an authors'-side convenience that SSHes to our Rice cluster (hostnames \texttt{odyssey}, \texttt{illyad}, \texttt{headroom}) and is \emph{not} portable to other sites; reviewers should skip it. Figure~5 and Table~V reproduce without any GPU.

\textbf{Network egress required:} \path{pypi.org} and \path{pypi.nvidia.com} (step 2 dependency install); \path{github.com} or \path{zenodo.org} (step 3 data download); \path{openrouter.ai} (Table~V only). Firewall-restricted sites should pre-request exceptions.

\textbf{Third-party licenses.} Benchmarks under \path{benchmarks/} retain their upstream licenses (see \path{benchmarks/*/LICENSE} in the artifact); the LEO analysis code itself is released under Apache License 2.0.

\artcomp

All reproduction paths rely on the pre-collected profiling data shipped with the artifact, so profiling ($T_1$) is skipped; see the AD for the full end-to-end pipeline if fresh GPU profiling is desired. Figure~5 and Table~V are CPU-only and fully independent; Table~IV and the Section~VI case studies share per-vendor Docker images and may run in parallel across GPU hosts.

\begin{table*}[t]
\caption{AE reproduction map: each paper element, its entry-point script, and expected wall-clock on a single host.}
\label{tab:ae-map}
\centering
\footnotesize
\begin{tabular}{@{}llc@{}}
\toprule
Paper element & Entry point & Wall-clock \\
\midrule
Figure~5 (SDC coverage)       & \path{scripts/collect_sdc.sh}                         & 5--10 min (CPU only) \\
Table~IV (per-kernel speedups) & \path{scripts/evaluation/run_workload_rajaperf.sh}    & 2--4 h per vendor (GPU) \\
Section~VI case studies        & \path{benchmarks/<name>/run_compare.sh}               & per-benchmark (GPU) \\
Table~V (LLM diagnostics)      & \texttt{python -m scripts.validation.main --llm-eval} & 10--20 min (CPU only) \\
\bottomrule
\end{tabular}
\end{table*}

\textbf{Known Deviations.} Before executing the commands below, note the following non-determinism caveats and tolerance windows:
\begin{itemize}
\item \textbf{Determinism.} LEO output is byte-identical across repeated runs on the same measurement database; archived HPCToolkit timestamps are historical and do not affect analysis results.
\item \textbf{Intel PVC variability.} Runtime noise on GPU Max~1100 is higher than on NVIDIA/AMD (median CV $\sim$9\%). Use the $\pm$9\% tolerance when comparing Table~IV Intel speedups.
\item \textbf{Minimum reproduction target.} Reviewers with access to a single vendor fit inside SC26's 8-hour AE budget and can earn \emph{Results Reproduced} credit on that vendor: NVIDIA GH200 or AMD MI300A alone reproduces all 21 rows of Table~IV for that column in $\sim$2--4~h; Intel PVC reproduces 18 rows (Kripke, llama.cpp, QuickSilver lack SYCL ports and are marked N/A). Per-vendor runs are independent; multi-vendor reproduction is parallelizable across separate GPU hosts.
\item \textbf{LLM sampling variance.} The semantic-match proxy produced by \path{--llm-eval} is non-deterministic at temperature~0.7; repeated invocations may differ per-kernel, but the relative ranking of C vs.\ C+S vs.\ C+L(S) is stable. The paper's Compilable / Geomean Speedup / Regressions columns come from a separate compile-and-benchmark harness (not bundled); this artifact does not reproduce those numbers.
\end{itemize}

\textbf{Figure~5 --- SDC coverage (CPU-only, $\sim$5--10~min).}
Run \texttt{bash}~\path{scripts/collect_sdc.sh}. LEO analyzes pre-collected HPCToolkit databases and streams per-kernel SDC (before/after LEO pruning) to stdout; output consumed by \path{scripts/plot_sdc_paper.py}.

\textbf{Table~IV --- per-kernel speedups (requires GPU, $\sim$2--4~h per vendor).}
Run \texttt{bash}~\path{scripts/evaluation/run_workload_rajaperf.sh}~\texttt{--kernel <K> --vendor <V>} (\texttt{<V>} $\in$ \texttt{\{nvidia,~amd,~intel,~all\}}); compute speedups via \texttt{cd}~\path{benchmarks/rajaperf-h100}~\texttt{\&\& python postprocess.py}.

\textbf{Section~VI case studies (requires GPU).}
RAJAPerf-tree kernels reuse the Table~IV entry point. Out-of-tree benchmarks live under \path{benchmarks/<name>/} and follow one of two patterns. (a)~Self-contained split (miniBUDE, XSBench, LULESH, and the rajaperf-h100 mirror of Table~IV): both \path{original/} and \path{optimized/} trees are vendored, so \texttt{diff -ruN original/ optimized/} shows the LEO change directly. (b)~Upstream-clone + patch (QuickSilver, llama.cpp, Kripke): the \path{optimized/} directory contains the modified files (and for llama.cpp / Kripke, explicit \path{*.patch} files); the per-benchmark \texttt{README.md} gives the upstream repo URL (pinned to the \texttt{master} branch at submission time) and a one-line \texttt{git clone} to obtain the baseline for diffing. Each benchmark has a \texttt{run\_compare.sh} (or per-vendor \texttt{run\_compare\_<vendor>.sh}) entry point.

\textbf{Table~V --- LLM diagnostic study (CPU-only, $\sim$10--20~min, optional).}
Export \path{OPENROUTER_API_KEY}; run \path{uv run python -m scripts.validation.main --llm-eval --llm-model google/gemini-3.1-pro --llm-log results/llm_eval.log}. Pre-collected LLM outputs are in \texttt{results/}; lower \path{--llm-concurrency} (default~5) if rate-limited.

\artout

\begin{itemize}
\item \textbf{Figure~5:} \path{scripts/collect_sdc.sh} writes a deterministic per-kernel SDC-coverage text table to stdout. Reviewers can verify byte-identical reproduction with \texttt{sha256sum -c sdc\_coverage\_reference.txt.sha256} (reference output and checksum are committed at the artifact root). \path{scripts/plot_sdc_paper.py} then emits the paper's grouped bar chart. Expected NVIDIA coverage: 30\%--74\% before pruning, 64\%--94\% after; AMD and Intel ranges documented in the artifact README.
\item \textbf{Table~IV:} \path{benchmarks/rajaperf-h100/postprocess.py} emits a per-kernel speedup CSV and per-vendor geometric means. Tolerance: $\pm$5\% on NVIDIA~GH200 and AMD~MI300A (median CV below 1\%); $\pm$9\% on Intel~PVC (median CV $\sim$9\% due to platform variability).
\item \textbf{Table~V (semantic-match proxy only):} \path{--llm-eval} prints per-kernel scores with confidence levels (Low/Medium/High) and a summary line with average score, high-confidence count, and evaluated-vs-total fractions; \path{--llm-log} captures raw LLM responses. Reproducing Table~V's Compilable / Speedup / Regressions columns requires the separate compile-and-benchmark harness (not bundled).
\item \textbf{Case studies (Section~VI):} qualitative; each per-benchmark \texttt{README.md} plus the diff between \texttt{original/} and \texttt{optimized/} (or upstream commit and patch pair, where applicable) documents the LEO-guided change.
\item \textbf{Troubleshooting:} see \path{docs/TROUBLESHOOTING.md} in the artifact for common issues (HPCToolkit build, Docker vendor bases, GPU drivers, GTPin).
\end{itemize}

\end{document}
